\section{Numerical Experiments}
In this section, the LP and SDP relaxations as well as rounding schemes introduced in Sections \ref{sec:lpRelax} and \ref{sec:sdpRelax} are put to the test for key CSP problems, such as Max-Cut and Max k-SAT. This section provides empirical validation and identifies their usefulness in practical applications. In particular, this section contains numerical studies for the LP relaxation and the Max k-SAT rounding scheme and the SDP relaxation in combination with the Goeman-Williamson rounding scheme for Max Cut. 

\subsection{LP Relaxation and Rounding scheme for Max k-SAT}
The LP relaxation as introduced in Section \ref{sec:lpRelax} can be applied to any CSP. However, it does not provide a feasible solution to the CSP ( unless the optimal solution happens to be feasible for CSP) since the LP is a relaxation of a CSP. Therefore, its application is dependent on a technique to generate feasible solutions from the LP solution. Such a technique was introduced for K-SAT in Section \ref{sec:lpRoundingSat}. In this section, results are presented of applying the LP relaxation and the rounding scheme to Max 3-SAT on randomly generated 3-SAT instances using CVX.

The 3-SAT instances where generated as follows:
\begin{enumerate}
	\item A solution $x^*$ on $k$ variables is generated. Each variable is independently set to $1$ or $0$, where $1$ is chosen with probability $p_T$. $p_T$ is the probability of setting a variable to true. This is probability is drawn from a uniform distribution on $[0,1]$. 
	\item $m$ constraints are added. These constraints are constructed via the following procedure:
	\begin{enumerate}
		\item The number of negated variables in the scope is uniformly drawn from $[0,1,2,3]$.
		\item For the scope, 3 variables are randomly drawn with replacement.
		\item A constraint is accepted if the feasible solution satisfies the constraint and rejected otherwise.
	\end{enumerate}
\end{enumerate}

\begin{table}
	\footnotesize
	\centering
	\caption{Experimental results for 3-SAT Problem using LP relaxation and LP Rounding for SAT. Values reported are averages of 50 randomly generated instances. $z^*$ is the optimal value of the CSP, $z^*_{LP}$ is the LP optimal value, $z^*_{round}$ is the optimal value of the feasible solution generated by the rounding. $t_{gen}$ is the time to generate the problem instance, $t_{solve}$ is the time to construct the CVX formulation and solve the problem, and $t_{round}$ is the time to round the solution of the relaxation to create a feasible CSP solution. }
	\vspace{.3cm}
	\begin{tabularx}{\textwidth}{>{\centering}p{1.7cm}>{\centering}p{1.7cm}ssCCmC}
		\toprule
		Number of variables & Number of constraints & Mean $z^*$ (s.d.) & Mean $z^*_{LP}$ (s.d.) & Mean $z^*_{round}$ (s.d.) & Mean $t_{gen}$ (s.d.) & Mean $t_{solve}$ (s.d.) & Mean $t_{round}$ (s.d.) \\ \midrule
		10  & 20  & 1 (0) & 1 (0) & 0.89 (0.08) & 0.032 (0.006) & 0.78 (0.03) & 0.00 (0.00) \\
		10  & 50  & 1 (0) & 1 (0) & 0.89 (0.05) & 0.08 (0.01)   & 1.51 (0.04) & 0.00 (0.00) \\
		20  & 40  & 1 (0) & 1 (0) & 0.88 (0.05) & 0.066 (0.008) & 1.29 (0.05) & 0.00 (0.00) \\
		20  & 100 & 1 (0) & 1 (0) & 0.89 (0.04) & 0.19 (0.02)   & 2.8 (0.2)   & 0.00 (0.00) \\
		50  & 50  & 1 (0) & 1 (0) & 0.89 (0.04) & 0.08 (0.01)   & 1.58 (0.05) & 0.00 (0.00) \\
		50  & 100 & 1 (0) & 1 (0) & 0.89 (0.03) & 0.19 (0.03)   & 2.81 (0.06) & 0.00 (0.00) \\
		50  & 200 & 1 (0) & 1 (0) & 0.88 (0.02) & 0.50 (0.08)   & 5.5 (0.3)   & 0.00 (0.00) \\
		100 & 100 & 1 (0) & 1 (0) & 0.90 (0.04) & 0.20 (0.03)   & 3.0 (0.1)   & 0.00 (0.00) \\
		100 & 200 & 1 (0) & 1 (0) & 0.88 (0.02) & 0.6 (0.1)     & 7 (1)       & 0.00 (0.00) \\
		\bottomrule
	\end{tabularx}
	\label{tab:expSat}
\end{table}

The results of the experiments are reported in Table \ref{tab:expSat}. It is observed that generating the CVX formulation as well as solving the LP is the bottleneck. As expected, this increases when the problem instances become large. Furthermore, note that the proven bound of $0.63$ is indeed satisfied. This is an empirical verification of the stated theorem.

\subsection{Experiments with Max-Cut}
In this section, we generate several Max-Cut problem instances and then compare the results using LP relaxation and SDP relaxation. We also present empirical results for the schemes namely LP Rounding (Section \ref{sec:lpRoundingSat}) and GW Rounding (Section \ref{GWAlgo}). 

The Max-Cut instances were generated as follows. We provide set of vertices $(V)$, and the number of edges as the input $(E)$. Next, 
\begin{enumerate}
	\item We randomly partition the variable set into two disjoint subsets. For $|V|$ variables, we do this by selecting uniformly at random $[|V|/2]$ variables independently from $V$ and declaring them as one set and its complement as the other set, call them $V_1$ and $V_2$. 
	\item We generate a weight vector of size $E$, with all entries drawn i.i.d. from a Uniform distribution on $[0, 1]$. We normalize the weights so that they sum to $1$. Call this $\{ w_i : i = 1, \ldots, E\}$.
	\item For $i=1, \ldots, E$ 
	\begin{enumerate}
		\item  Select uniformly at random one node each from the sets $V_1$ and $V_2$ independently. 
		\item Declare an edge between these two nodes and set the edge weight to $w_{i}$.
	\end{enumerate}
\end{enumerate}
In this fashion, we are able to generate a random instance of a bipartite graph with random edge weights that sum to $1$. Some pair of the vertices may get selected multiple times, but that is equivalent to increasing the weight for the edge between them (and hence no conflict).

The way we generate the problem instances, they do have an optimal cut and hence in either relaxation schemes, the optimal value will be $1$. Hence, we only compare the results for the effectiveness of the two rounding schemes, by listing the value that we obtain by randomly rounding the solution that we obtain from the relaxations. 

As for the previous set up, we use CVX for solving the convex problem in either relaxation. We have following comments on the results that are tabulated in Table \ref{tab:maxlp} for the LP Relaxation and Table \ref{tab:maxgw} for the SDP relaxation. 
\begin{itemize}
\item For the LP relaxation, the round value is around $0.5$ which is same as for a random assignment suggesting that LP rounding doesn't work very well for the Max-Cut. 
\item The Goemans and Williamson Rounding scheme works very well for \emph{almost all} instances which was quite surprising, nevertheless we think that owes justification in the fact that we tested them only on bipartite graphs. It is worthwhile to note that for bipartite graphs there exists a deterministic algorithm which runs in linear time to give us the optimal cut, and in our case this random scheme seems to be almost equally good. 
\end{itemize}

\begin{table}
	\footnotesize
	\centering
	\caption{Experimental results for Max-Cut Problem Instances using LP relaxation and LP rounding. Values reported are averages of 50 randomly generated instances. $z^*$ is the optimal value of the CSP, $z^*_{LP}$ is the LP optimal value, $z^*_{round}$ is the optimal value of the feasible solution generated by the rounding. $t_{gen}$ is the time to generate the problem instance, $t_{solve}$ is the time to construct the CVX formulation and solve the problem, and $t_{round}$ is the time to round the solution of the relaxation to create a feasible CSP solution. }
	\vspace{.3cm}
	\begin{tabularx}{\textwidth}{>{\centering}p{1.7cm}>{\centering}p{1.7cm}ssCCmC}
		\toprule

		
		Number of variables & Number of constraints & Mean $z^*$ (s.d.) & Mean $z^*_{LP}$ (s.d.) & Mean $z^*_{round}$ (s.d.) & Mean $t_{gen}$ (s.d.) & Mean $t_{solve}$ (s.d.) & Mean $t_{round}$ (s.d.) \\ \midrule
    5 					& 4    						& 1(0) & 1(0) 		& 0.5(0.3)		& 0.47(0.03)	& 0.0022(0.0004)   	& 0.00(0.00)\\
    10					& 50  						& 1(0) & 1(0) 		& 0.5(0.1)		& 0.89(0.02)	& 0.016(0.003)	  	& 0.00(0.00)\\
    20					& 40  						& 1(0) & 1(0) 		& 0.50(0.08)	& 0.8(0.2)		& 0.012(0.003)	  	& 0.00(0.00)\\
    20					& 100 						& 1(0) & 1(0) 		& 0.50(0.07)	& 1.3(0.1)		& 0.026(0.004)	  	& 0.00(0.00)\\
    50					& 50  						& 1(0) & 1(0) 		& 0.51(0.07)	& 0.88(0.1)		& 0.015(0.002)	  	& 0.00(0.00)\\
    50					& 100 						& 1(0) & 1(0) 		& 0.51(0.05)	& 1.30(0.04)	& 0.025(0.003)	  	& 0.00(0.00)\\
    50					& 200 						& 1(0) & 1(0) 		& 0.50(0.04)	& 2.3(0.3)		& 0.05(0.02)	  	& 0.00(0.00)\\
    100 				& 100	 					& 1(0) & 1(0) 		& 0.51(0.06)	& 1.38(0.06)	& 0.025(0.003)	  	& 0.00(0.00)\\
    100 				& 200	 					& 1(0) & 1(0) 		& 0.50(0.04)	& 2.4(0.2)		& 0.0461(0.003)	  	& 0.00(0.00)\\
 \bottomrule
	\end{tabularx}      
	\label{tab:maxlp}                                                                                                                            
\end{table}




\begin{table}
	\footnotesize
	\centering
	\caption{Experimental results for Max-Cut Problem Instances using SDP relaxation  from Section \ref{maxcut} and GW rounding from Section \ref{GWAlgo}. Values reported are averages of 50 randomly generated instances. $z^*$ is the optimal value of the CSP, $z^*_{GW}$ is the SDP optimal value, $z^*_{round}$ is the optimal value of the feasible solution generated by the rounding. $t_{gen}$ is the time to generate the problem instance, $t_{solve}$ is the time to construct the CVX formulation and solve the problem, and $t_{round}$ is the time to round the solution of the relaxation to create a feasible CSP solution. }
	\vspace{.3cm}
	\begin{tabularx}{\textwidth}{>{\centering}p{1.7cm}>{\centering}p{1.7cm}ssCCmC}
		\toprule
		

		Number of variables & Number of constraints & Mean $z^*$ (s.d.) & Mean $z^*_{GW}$ (s.d.) & Mean $z^*_{round}$ (s.d.) & Mean $t_{gen}$ (s.d.) & Mean $t_{solve}$ (s.d.) & Mean $t_{round}$ (s.d.) \\ \midrule
    5 					& 4    						& 1(0) & 1(0) 		& 1(0)				& 0.46(0.03)			& 0.0022(0.0004) & 0.00(0.00) \\
    10					& 50  						& 1(0) & 1(0) 		& 1(0)				& 0.46(0.04)			& 0.016(0.003)	 & 0.00(0.00)\\
    20					& 40  						& 1(0) & 1(0) 		& 1.00(0.03)		& 0.40(0.12)			& 0.012(0.003)	 & 0.00(0.00)\\
    20					& 100 						& 1(0) & 1(0) 		& 1(0)				& 0.34(0.04)			& 0.026(0.004)	 & 0.00(0.00)\\
    50					& 50  						& 1(0) & 1(0) 		& 1(0)				& 0.42(0.04)			& 0.015(0.002)	 & 0.00(0.00)\\
    50					& 100 						& 1(0) & 1(0) 		& 1(0)				& 0.41(0.05)			& 0.025(0.003)	 & 0.00(0.00)\\
    50					& 200 						& 1(0) & 1(0) 		& 1(0)				& 0.39(0.04)			& 0.05(0.02)	 & 0.00(0.00)\\
    100 				& 100	 					& 1(0) & 1(0) 		& 1(0)				& 0.55(0.04)			& 0.025(0.003)	 & 0.00(0.00)\\
    100 				& 200	 					& 1(0) & 1(0) 		& 1(0)				& 0.62(0.08)			& 0.0461(0.003)	 & 0.00(0.00)\\

 \bottomrule
	\end{tabularx}            
	\label{tab:maxgw}                                                                                                                      
\end{table}


